
This work systematically compares MC-Dropout and SWAG for uncertainty quantification, revealing a
fundamental trade-off between computational efficiency and and the quality of uncertainty estimates.
MC-Dropout's advantages lie in computational efficiency, generating uncertainty estimates through simple
stochastic forward passes. It however shows limitations including undercoverage and overconfidence under
distribution shift. SWAG addresses these issues through SGD-based weight-space exploration, yielding
better-calibrated uncertainties with improved responsiveness to distributional changes, but requiring
extended training and increased memory overhead.

\vspace{0.15cm}
Given these differences, our findings suggest practical recommendations for choosing between MC-Dropout and
SWAG. MC-Dropout suits applications prioritizing speed and simplicity where uncertainties play a secondary
role, particularly in stable environments. Its deficient OOD performance (Table \ref{tab:ood_results})
makes it unsuitable for safety-critical systems. SWAG proves preferable when the reliability of uncertainty
is central to decision making, especially where training budget permits extended exploration and deployment
contexts involve potential distribution shifts.

\vspace{0.15cm}
Looking ahead, both methods present opportunities for improvement. Extensions of MC-Dropout could reduce
its overconfidence through techniques such as Concrete Dropout \citep{gal2017concretedropout}, which learns
layer-specific retention probabilities to better calibrate uncertainty. SWAG can be further improved in
terms of expressiveness and efficiency. MultiSWAG \citep{onal2024multiswag}, for instance, ensemble the
several independently trained SWAG models to approximate multimodal posteriors, while SWALP
\citep{yang2019swalp} enables low-precision inference, reducing computational cost without degrading
performance. For applications where multimodality capture is essential, Deep Ensembles
\citep{lakshminarayanan2017preduncw/deepensembles} remain superior despite high computational costs,
with MultiSWAG offering a promising balance between efficiency and robustness.

\vspace{0.15cm}
The selection of an uncertainty quantification method should ultimately be guided by the specific
requirements of the target application. MC-Dropout is well suited for lightweight and scalable solutions,
SWAG for reliable calibration, and ensemble variants where resources permit robust uncertainty modeling.
